The Hyperedge Event Model

### 2018-05-25 paper/ba-HEM/ba-sample.tex
revisions except conclusion and updated plots

%
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[algo2e]{algorithm2e}
\usepackage{algorithmic}  
\usepackage{algorithm}
\usepackage{mathtools}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\def\spacingset#1{\renewcommand{\baselinestretch}%
	{#1}\small\normalsize} \spacingset{1}
\usepackage{fmtcount}
\startlocaldefs
\numberwithin{equation}{section}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\endlocaldefs
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\begin{document}

@@

\begin{keyword}
\kwd{sample}
\kwd{\LaTeXe}
\end{keyword}

@@

   \begin{figure}[ht]

@@

   	\includegraphics[width=1\textwidth]{img/GiRplot-1.png}	

@@

 	   we formulate the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$ and ground them in illustrative examples. We then report a suite of experiments that test the HEM's ability to form the posterior distribution over its latent variables. 

@@

	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using log-normal distribution, which shows better performance in Section \ref{subsec:Experiment_email}. Upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic data, where the left one for outdegree statistic and the right plot is for indegree statistic. For both plots, the x-axis represents the nodes ($A=1,\ldots,18$), and the y-axis represents the number of emails sent or received by the node. When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes. For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, showing acceptable fit to the data. Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better. Since we use more information in the receiver selection process (i.e., network effects) while we rely solely on minimum time increments when choosing the observed sender, these results are expected. Lower left plot is the distribution of receiver sizes, where the x-axis spans over the size of receivers 1 to 14 (which is the maximum size of observed receivers) and the y-axis denotes the number of emails with x-number of receivers. The result shows that our model is underestimating emails with one receiver while overestimating emails with two, three, and four receivers. One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the emails with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right. To improve the goodness of fit for receiver sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$. In the end, the plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions against each other in order to assess how closely two data sets agree. Here, the closeness to the diagonal line gives a measure of the difference between the distribution of simulated time increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution. All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the comparison between log-normal and exponential distributions are attached in Appendix C.
	\begin{figure}[!t]
		\centering
		\includegraphics[width=0.495\textwidth]{img/outdegreenew-1.png}	
		\includegraphics[width=0.495\textwidth]{img/indegreenew-1.png}	
		\includegraphics[width=0.495\textwidth]{img/recipientsizenew-1.png}	
		\includegraphics[width=0.31\textwidth]{img/timeppnew.pdf}
		\caption {PPC results from log-normal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and PP plot for time increments (\textit{lower right}). Blue lines denote the observed statistics (in the first three plots) or the diagonal line connecting $(0, 0)$ and $(1, 1)$ (in the last plot).}
		\label{figure:PPCresults}
	\end{figure}

@@

	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we choose to analyze Montgomery county email data and interpret the results using log-normal distribution. We assume weakly informative priors for latent variables such as $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b=\boldsymbol{0}, \Sigma_b = 2\times I_P)$, $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta=\boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, and $\sigma_\tau^2 \sim \mbox{inverse-Gamma}(a=2, b=1)$, and run MCMC algorithm in Algorithm \ref{alg:MCMC} with $O=55,000$ outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample. While the inner iterations for $\sigma_\tau^2$ is fixed as 1, we specify the inner iterations $I_1=20$ for $\boldsymbol{b}$ and $I_2=10$ for $\boldsymbol{\eta}$ to adjust for slower convergence rates. Convergence diagnostics including some traceplots and Geweke diagnostics \citep{geweke1991evaluating} are provided in Appendix D.

@@

	For timestamp covariates, Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{\eta}$. Since we assume log-normal distribution for time increments, the interpretation of $\hat{\boldsymbol{\eta}}$ should be based on

@@

	To begin with, the posterior estimates of two temporal effects---weekend and pm---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after 12pm, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am). On the contrary, the statistics manager, outdegree, and indegree turn out to shorten the time to next email. For example, being a county manager (i.e., the manager of the managers) lowers the expected $\log(\tau_{ad})$ by -1.070, since he or she needs to respond fastly to emails with important decisions. In addition, the manager in general sends or receives a lot more emails which may shorten the response time. This argument is supported by the posterior estimates for outdegree and indegree, where the estimated coefficients are approximately -0.206 and -0.060, respectively. Gender of the department manager is shown to have no significant effect on time-to-next-email. The posterior mean estimate of the variance parameter $\sigma^2_\tau$ is 14.093 with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time increments in this data.

@@

\section*{Appendix}
	\subsection*{Appendix A: Alternative Generative Process} \label{appendix:alternativeGP}
		\begin{algorithm}[!ht]
			\SetAlgoLined
			\caption{Generative Process: one receiver and one or more senders}
			\begin{algorithmic}
			\STATE \textbf{Input}: number of edges and nodes $(D, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and the coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
							\vskip 0.1in				
				\FOR{d=1 to D}
				\FOR{r=1 to $A$}
				\FOR{a=1 to $A$ (a $\neq$ r)}
				\STATE	set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
				\ENDFOR
				\STATE	draw $\boldsymbol{u}_{rd}  \sim
				\mbox{MB}_G(\boldsymbol{\lambda}_{rd})$
				\STATE		set $\mu_{rd} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{rd})$
				\STATE		draw $\tau_{rd} \sim f_\tau(\mu_{rd}, \sigma_\tau^2)$
				\ENDFOR
				\IF {$n \geq 2$ tied events} 
				\STATE	set ${r}_d=\mbox{argmin}_{r}(\tau_{rd})$
				\STATE	set $\boldsymbol{a}_d=\boldsymbol{u}_{r_d d},\ldots,\boldsymbol{a}_{d+n-1}= ,\boldsymbol{u}_{r_{d+n-1} d}$
				\STATE	set $t_d, \ldots, t_{d+n-1}=t_{d-1} + \min_r\tau_{rd}$
				\STATE		jump to $d = d+n$
				\ELSE
				\STATE	set ${r}_d = \mbox{argmin}_{r}(\tau_{rd}) $
				\STATE	set $\boldsymbol{a}_d= \boldsymbol{u}_{r_d d}$
				\STATE	set $t_d =t_{d-1} + \min_r\tau_{rd}$
				\ENDIF
				\ENDFOR
			\end{algorithmic}
			\label{alg:generative2}
		\end{algorithm}
	\subsection*{Appendix B: Normalizing Constant of MB$_{G}$}\label{appendix: non-empty Gibbs measure}
	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure---defines the probability of sender $a$ selecting the binary receiver vector $\boldsymbol{u}_{ad}$ as
	\begin{equation*} 
	\begin{aligned}
	& \Pr(\boldsymbol{u}_{ad}|\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big),
	\end{aligned}
	\end{equation*}
	where the receiver intensity is a linear combination of edge covariates---i.e., $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$---as defined in Secton \ref{subsec: Tie}.

@@

			\includegraphics[width=0.495\textwidth]{img/outdegree_two-1.png}	
			\includegraphics[width=0.495\textwidth]{img/indegree_two-1.png}	
			\includegraphics[width=0.495\textwidth]{img/recipientsize_two-1.png}	
			\includegraphics[width=0.31\textwidth]{img/timepp_two-1.png}
			\caption {Comparison of PPC results between log-normal (\textit{red}) and exponential (\textit{green}) distributions: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and PPplot for time increments (\textit{lower right}). Blue lines denote the observed statistics (in the first three plots) or the diagonal line connecting $(0, 0)$ and $(1, 1)$ (in the last plot).}

@@

		\includegraphics[width=0.495\textwidth]{img/betatrace.pdf}	
		\includegraphics[width=0.495\textwidth]{img/etatrace.pdf}	
		\includegraphics[width=0.495\textwidth]{img/betageweke.pdf}	
		\includegraphics[width=0.44\textwidth]{img/etageweke.pdf}
		\caption {Convergence diagnostics from log-normal distribution: traceplots and density plots for $\boldsymbol{b}$ chains (\textit{upper left}) and $\boldsymbol{\eta}$ chains (\textit{upper right}), and geweke diagnostics for $\boldsymbol{b}$ chains (\textit{lower left}) and $\boldsymbol{\eta}$ chains (\textit{lower right}).}

@@

\begin{supplement}
\sname{Supplement A}\label{suppA} 
\stitle{Title of the Supplement A}
\slink[url]{http://www.some-url-address.org/dowload/0000.zip}
\sdescription{Add description for supplement material.}
\end{supplement}

>>>>

%
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[algo2e]{algorithm2e}
\usepackage{algorithmic}  
\usepackage{algorithm}
\usepackage{mathtools}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}

\def\spacingset#1{\renewcommand{\baselinestretch}%
	{#1}\small\normalsize} \spacingset{1}
\usepackage{fmtcount}
\startlocaldefs
\numberwithin{equation}{section}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\endlocaldefs
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\begin{document}

@@

\begin{keyword}
\kwd{continuous time network model} 
\kwd{email data analysis}
\end{keyword}

@@

@@

   	\begin{subfigure}[b]{0.2425\textwidth}
   		   	\caption{Mean of $\lVert \boldsymbol{r}_{d} \rVert_1 $}
   	\includegraphics[width=\textwidth]{img/plot1.png}	
   	\end{subfigure}
   	   	\begin{subfigure}[b]{0.2425\textwidth}
   	   		   		   	\caption{Variance of $\lVert \boldsymbol{r}_{d} \rVert_1 $}
   	   		\includegraphics[width=\textwidth]{img/plot2.png}	
   	   	\end{subfigure}
   	   	   	\begin{subfigure}[b]{0.2425\textwidth}
   	   	   		   	   	   		\caption{Mean of $\tau_d$}
   	   	   		\includegraphics[width=\textwidth]{img/plot3.png}	
   	   	   	\end{subfigure}
   	   	   	   	   	   	\begin{subfigure}[b]{0.2425\textwidth}
   	   	   	   	   	   		  	\caption{Variance of $\tau_d$}
   	   	   	   	   	   		\includegraphics[width=\textwidth]{img/plot4.png}	
   	   	   	   	   	   	\end{subfigure}
   	   	   	   	   	   	   	   	   	   	\begin{subfigure}[b]{0.2425\textwidth}
   	   	   	   	   	   	   	   	   	   		\caption{Value of $b_1$}
   	   	   	   	   	   	   	   	   	   		\includegraphics[width=\textwidth]{img/plot5.png}	
   	   	   	   	   	   	   	   	   	   	\end{subfigure}
   	   	   		   	   	\begin{subfigure}[b]{0.2425\textwidth}
   	   	   		   	   		\caption{Value of $b_2$}
   	   	   		   	   		\includegraphics[width=\textwidth]{img/plot6.png}	
   	   	   		   	   	\end{subfigure}   	   	   	   	   	   	   	
   		   	   	\begin{subfigure}[b]{0.2425\textwidth}
   		   	   		\caption{Value of $b_3$}
   		   	   		\includegraphics[width=\textwidth]{img/plot7.png}	
   		   	   	\end{subfigure}   	   		   	   	
   		   	   	   		   	   	\begin{subfigure}[b]{0.2425\textwidth}
   		   	   	   		   	   		\caption{Value of $b_4$}
   		   	   	   		   	   		\includegraphics[width=\textwidth]{img/plot8.png}	
   		   	   	   		   	   	\end{subfigure}   	   		   	   	
   		   	   	   		   	   	   		   	   	\begin{subfigure}[b]{0.2425\textwidth}
   		   	   	   		   	   	   		   	   		\caption{Value of $\eta_1$}
   		   	   	   		   	   	   		   	   		\includegraphics[width=\textwidth]{img/plot9.png}	
   		   	   	   		   	   	   		   	   	\end{subfigure}   	   		   	   	
   		     		   	   	\begin{subfigure}[b]{0.2425\textwidth}
   		     		   	   		\caption{Value of $\eta_2$}
   		     		   	   		\includegraphics[width=\textwidth]{img/plot10.png}	
   		     		   	   	\end{subfigure}   	   		   	   	
   		   	     		   	   	\begin{subfigure}[b]{0.2425\textwidth}
   		   	     		   	   		\caption{Value of $\eta_3$}
   		   	     		   	   		\includegraphics[width=\textwidth]{img/plot11.png}	
   		   	     		   	   	\end{subfigure}   	   		   	   	  		   	   	 	
   		   	     		   	   		     		   	   	\begin{subfigure}[b]{0.2425\textwidth}
   		   	     		   	   		     		   	   		\caption{Value of $\sigma^2_\tau$}
   		   	     		   	   		     		   	   		\includegraphics[width=\textwidth]{img/plot12.png}	
   		   	     		   	   		     		   	   	\end{subfigure}   	   		   	   	   	   		   	   	   		   	   	

@@

 	   we formulate the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$ and ground them in illustrative examples. We then report a suite of experiments---out-of-sample prediction for model selection and posterior predictive checks---that test the HEM's ability to form the posterior distribution over its latent variables. Finally, we demonstrate an exploratory analysis of Montgomery County email data using the model estimates to discover interesting patterns in organizational communication networks.

@@

	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using log-normal distribution, which shows better performance in Section \ref{subsec:Experiment_email}. Upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic data, where the left one for outdegree statistic and the right plot is for indegree statistic. For both plots, the x-axis represents the nodes ($A=1,\ldots,18$), and the y-axis represents the number of emails sent or received by the node. When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes. For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, showing acceptable fit to the data. Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better. Since we use more information in the receiver selection process (i.e., network effects) while we rely solely on minimum time increments when choosing the observed sender, these results are expected. Lower left plot is the distribution of receiver sizes, where the x-axis spans over the size of receivers 1 to 14 (which is the maximum size of observed receivers) and the y-axis denotes the number of emails with x-number of receivers. The result shows that our model is underestimating emails with one receiver while overestimating emails with two, three, and four receivers. One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the emails with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right. To improve the goodness of fit for receiver sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$. In the end, the plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions---one for simulated time increments and another for observed time increments---against each other in order to assess how closely two data sets agree. Here, the closeness to the diagonal line connecting $(0, 0)$ and $(1, 1)$ gives a measure of difference between the simulated and observed time increments, and our PP plot shows that we have great performance in reproducing the observed time distribution. All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are attached in Appendix C.
	\begin{figure}[!htb]
		\centering
		\begin{tabular}[t]{cc}
		   	\begin{subfigure}[b]{0.495\textwidth}
		   		\caption{Outdegree distribution}
		\includegraphics[width=\textwidth]{img/outdegreenew-1.png}	
		   	\end{subfigure}
		   			   	\begin{subfigure}[b]{0.495\textwidth}
		   			   		\caption{Indegree distribution}
		   			   		\includegraphics[width=\textwidth]{img/indegreenew-1.png}	
		   			   	\end{subfigure}\\
			   	\begin{subfigure}[b]{0.495\textwidth}
			   		\caption{Receiver size distribution}
			   		\includegraphics[width=\textwidth]{img/recipientsizenew-1.png}	
			   	\end{subfigure}
			   	\begin{subfigure}[b]{0.495\textwidth}
			   				\centering
			   		\caption{PPplot for time increments}
			   		\includegraphics[width=0.625\textwidth]{img/timeppnew.pdf}	
			   	\end{subfigure}
		\end{tabular}
		\caption {PPC results from log-normal distribution. Blue lines denote the observed statistics in (a)--(c) and denotes the diagonal line in (d).}
		\label{figure:PPCresults}
	\end{figure}

@@

	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we choose to analyze Montgomery county email data and interpret the results using log-normal distribution. We assume weakly informative priors for latent variables such as $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b=\boldsymbol{0}, \Sigma_b = 2\times I_P)$, $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta=\boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, and $\sigma_\tau^2 \sim \mbox{inverse-Gamma}(a=2, b=1)$, and run MCMC algorithm in Algorithm \ref{alg:MCMC} with $O=55,000$ outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample. While the inner iterations for $\sigma_\tau^2$ is fixed as 1, we specify the inner iterations $I_1=20$ for $\boldsymbol{b}$ and $I_2=10$ for $\boldsymbol{\eta}$ to adjust for slower convergence rates. Convergence diagnostics including the traceplots and Geweke diagnostics \citep{geweke1991evaluating} are provided in Appendix D.

@@

	For timestamp covariates, Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{\eta}$. Note that interpretations of the estimated coefficients for $\hat{\boldsymbol{\eta}}$ should be based on the specified timeunit of the datset, which we use ``hour" for Montgomery county email data. Moreover, since we assume log-normal distribution for time increments, we need careful interpretation regarding the timing equations

@@

	To begin with, the posterior estimates of two temporal effects---``weekend" and 		AM/PM"---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after midday, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am). On the contrary, the covariates ``manager", ``outdegree", and ``indegree" turn out to shorten the amount of time to next email. For example, being a county manager (i.e., the manager of department managers) lowers the expected value of $\log(\tau_{ad})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails. This argument is also supported by the posterior estimates for ``outdegree" and ``indegree" statistics, where the estimated coefficients are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively. Gender of the department manager is shown to have no significant effect on time increments. In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time increments of emails.

@@

\section*{Appendix}
	\subsection*{Appendix A: Alternative Generative Process} \label{appendix:alternativeGP}
		\begin{algorithm}[H]
			\SetAlgoLined
			\caption{Generative Process: one receiver and one or more senders}
			\begin{algorithmic}
			\STATE \textbf{Input}: number of edges and nodes $(D, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and the coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
							\vskip 0.1in				
				\FOR{d=1 to D}
				\FOR{r=1 to $A$}
				\FOR{a=1 to $A$ (a $\neq$ r)}
				\STATE	set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
				\ENDFOR
				\STATE	draw $\boldsymbol{u}_{rd}  \sim
				\mbox{MB}_G(\boldsymbol{\lambda}_{rd})$
				\STATE		set $\mu_{rd} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{rd})$
				\STATE		draw $\tau_{rd} \sim f_\tau(\mu_{rd}, \sigma_\tau^2)$
				\ENDFOR
				\IF {$n \geq 2$ tied events} 
				\STATE	set ${r}_d=\mbox{argmin}_{r}(\tau_{rd})$
				\STATE	set $\boldsymbol{a}_d=\boldsymbol{u}_{r_d d},\ldots,\boldsymbol{a}_{d+n-1}= ,\boldsymbol{u}_{r_{d+n-1} d}$
				\STATE	set $t_d, \ldots, t_{d+n-1}=t_{d-1} + \min_r\tau_{rd}$
				\STATE		jump to $d = d+n$
				\ELSE
				\STATE	set ${r}_d = \mbox{argmin}_{r}(\tau_{rd}) $
				\STATE	set $\boldsymbol{a}_d= \boldsymbol{u}_{r_d d}$
				\STATE	set $t_d =t_{d-1} + \min_r\tau_{rd}$
				\ENDIF
				\ENDFOR
			\end{algorithmic}
			\label{alg:generative2}
		\end{algorithm}
	\subsection*{Appendix B: Normalizing Constant of MB$_{G}$}\label{appendix: non-empty Gibbs measure}
	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure---defines the probability of sender $a$ selecting the binary receiver vector $\boldsymbol{u}_{ad}$ as
	\begin{equation*} 
	\begin{aligned}
	& \Pr(\boldsymbol{u}_{ad}|\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big),
	\end{aligned}
	\end{equation*}
	where the receiver intensity is a linear combination of edge covariates---i.e., $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$---as defined in Secton \ref{subsec: Tie}.

@@

			\begin{tabular}[t]{cc}
				\begin{subfigure}[b]{0.495\textwidth}
					\caption{Outdegree distribution}
					\includegraphics[width=\textwidth]{img/outdegree_two-1.png}	
				\end{subfigure}
				\begin{subfigure}[b]{0.495\textwidth}
					\caption{Indegree distribution}
					\includegraphics[width=\textwidth]{img/indegree_two-1.png}	
				\end{subfigure}\\
				\begin{subfigure}[b]{0.495\textwidth}
					\caption{Receiver size distribution}
					\includegraphics[width=\textwidth]{img/recipientsize_two-1.png}	
				\end{subfigure}
				\begin{subfigure}[b]{0.495\textwidth}
					\caption{PPplot for time increments}
					\includegraphics[width=0.625\textwidth]{img/timepp_two-1.png}
				\end{subfigure}
			\end{tabular}
			\caption {Comparison of PPC results between log-normal (\textit{red}) and exponential (\textit{green}) distributions. Blue lines denote the observed statistics in (a)--(c) and denotes the diagonal line in (d).}

@@

			\begin{tabular}[t]{cc}
				\begin{subfigure}[b]{0.495\textwidth}
					\caption{Traceplots of $\boldsymbol{b}$}
					\includegraphics[width=\textwidth]{img/betatrace.pdf}	
				\end{subfigure}
				\begin{subfigure}[b]{0.495\textwidth}
					\caption{Traceplot of $\boldsymbol{\eta}$}
					\includegraphics[width=\textwidth]{img/etatrace.pdf}	
				\end{subfigure}\\
				\begin{subfigure}[b]{0.495\textwidth}
					\caption{Geweke diagnostics for $\boldsymbol{b}$}
					\includegraphics[width=\textwidth]{img/betageweke.pdf}	
				\end{subfigure}
				\begin{subfigure}[b]{0.495\textwidth}
					\caption{Geweke diagnostics for $\boldsymbol{\eta}$ and $\sigma^2_\tau$}
					\includegraphics[width=0.89\textwidth]{img/etageweke.pdf}
				\end{subfigure}
			\end{tabular}
			\caption {Convergence diagnostics from log-normal distribution.}

@@

	\begin{supplement}
\sname{Supplement A}\label{suppA} 
\stitle{Title of the Supplement A}
\slink[url]{http://www.some-url-address.org/dowload/0000.zip}
\sdescription{Add description for supplement material.}
\end{supplement}
